Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
Oxford comma. Use it. Read 'Eats, Shoots, and Leaves' if you're not convinced @alex162

The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc. The \lamost\ data was shifted to rest frame and continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA. \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model. For details regarding the preparatory work, model generation and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}. The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.

>>>>

The data set of \LamostGiants\ \lamost\ giants was prepared by \citet{ho2017} for use with the supervised machine learning code \tc. The \lamost\ data was shifted to rest frame and continuum-normalised before it was resampled to a common uniform wavelength grid between 3905\,\AA\ and 9000\,\AA. \tc\ was used to infer $\teff$, $\logg$, [Fe/H], and [$\alpha$/Fe] using 9,952 stars in common between \lamost\ and the higher spectral resolution \apogee\ survey through the use of a data-driven spectral model. For details regarding the preparatory work, model generation, and label transfer between the APOGEE and LAMOST surveys, the reader is directed to \citet{ho2017}. The data-driven model generated by \textit{The Cannon} is treated in this study as the typical spectra for each star.
